Emory Cardiovscular Biobank

### 2021-05-31 Real_Data/Emory_Card_Biobank/Report.Rmd
Update ECB data analysis

# Primary Data Analysis of Metabolites

>>>>

## Primary Data Analysis of Metabolites
```{r eval=F}
train_dat %>% select(starts_with("mz")) %>% 
  summarise_all(var)
```

# Predictive Model

Outcome: `death3yr` (bin)
Covariates: None
Predictors: `starts_with("mz")`

```{r}
library(BHAM)
library(BhGLM)

mz_names <- train_dat %>% select(starts_with("mz")) %>% names

test_mz_names <- valid_dat  %>% select(starts_with("mz")) %>% names

sm_df <- data.frame(
  Var = mz_names,
 Func = "s",
 Args ="bs='cr', k=5"
)

sm_obj <- construct_smooth_data(sm_df, train_dat)

dsn_mat <- sm_obj$data

# The validation data doesn't overlap with training data
# test_sm_dat <- make_predict_dat(sm_obj$Smooth, dat = valid_dat)

mdl_defaul <- bmlasso(dsn_mat, train_dat$death3yr, family = "binomial")

mdl_dflt <- bmlasso_spline(dsn_mat, train_dat$death3yr, family = "binomial",
                           group = make_group(names(dsn_mat)))

measure.bh(mdl_defaul)

measure.bh(mdl_dflt)
```

## Validation
```{r eval = F}

measure.bh(mdl_defaul, new.x = test_sm_dat, new.y=valid_dat$death3yr)

measure.bh(mdl_dflt)
```
